Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-29 paper/paper-mainfile.tex
some high level introduction

\section{Introduction}
Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound. HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks. A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications. If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.

In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks. In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.

% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space. For some problems, such over-specification may remove all valid solutions.

Many problems might be naturally more suited to being modelled as POHTN problems. However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions. For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages. On the other hand, TOHTN planning is not expressive enough to model undecideable problems. Where this is possible, it results in lower worst-case solving time. Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.

Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case. % Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution. In fact, the state-of-the-art panda$_\pi$ planner and \cite{HTN2SAS} both use a compilation to classical planning, another decidable planning class.
In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems. We prove that when certain criteria are met, it guarantees that at least one solution will be preserved. 
Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion. Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.

\section{Hierarchical Planning Formalism}
Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning. There are many formalisations for HTN planning. The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}. HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning. TOHTN planning is a special case of POHTN planning.  % except with the initial task network replaced by a initial compound task.

A \textbf{Partially Ordered Hierarchical Planning}, also called POHTN, problem P = $(D, S_I, T_I)$
is defined over some domain $D$, 
has an initial state $S_I \in 2^F$, and 
has a initial compound task $T_I$. 
The closed world assumption also holds for HTN planning.

The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.

A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
T, which is a finite set of task identifiers (ids); 
$\singlePrec$, which is a partial order over T; and
$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.

% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
\begin{align}
tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
\end{align}
In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.

A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ... t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ... \alpha(t_n) \rangle$ in $S_I$ is executable.

%In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition. For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired. Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning. Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.

\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
%For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$. TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$. This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning. POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).

% As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.

\section{Inference of Preconditions and Effects}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other. This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.

\subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

@@

% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }

@@

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\

\todo{proven unsolvable should not be in superscripts}

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleCoverage}
	\scalebox{0.8} {
\begin{tabular}{lccccccl} 
	\toprule 
	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO\\  
	\midrule 
	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
			\midrule 
	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
			\midrule 
	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleCoverage}
	\scalebox{0.65} {
		\begin{tabular}{lccccccccccl} 
			\toprule 
			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
			&PO & TO & PO & TO  \\ 
\midrule 
Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
\midrule 
Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
\midrule 
Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
\bottomrule 
		\end{tabular}

@@

\begin{table}
	\centering
	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleIPC}
	\scalebox{0.7} {
\begin{tabular}{lccccccccccl} 
	\toprule 
	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
	&PO & TO & PO & TO  \\  
\midrule 
Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
\midrule 
Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
\midrule 
IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
\bottomrule 
\end{tabular} 
	}
\end{table}

>>>>

\section{Introduction}
\input{01--intro.tex}

\section{Hierarchical Planning Formalism}
\input{02--htn.tex}

\section{Inference of Preconditions and Effects}
\input{03--linearization-ground.tex}

The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other. This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.

\subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }

In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

@@

% visited checking with task sequences makes totally-ordered visited lists incomplete (with order)

@@

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleCoverage}
	\scalebox{0.8} {
\begin{tabular}{lccccccl} 
	\toprule 
	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO\\  
	\midrule 
	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
			\midrule 
	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
			\midrule 
	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleCoverage}
	\scalebox{0.65} {
		\begin{tabular}{lccccccccccl} 
			\toprule 
			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
			&PO & TO & PO & TO  \\ 
			\midrule 
			Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 0.0 & \textbf{17.0}  \\ 
			Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & 0.0 & \textbf{18.0}   \\ 
			Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}   \\ 
			PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 0.0 & 0.0   \\ 
			Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & 0.0 & 20.0   \\ 
			Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 0.0 & \textbf{25.0}   \\ 
			Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 2.0 & \textbf{35.0}   \\ 
			UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 0.0 & \textbf{21.0}   \\ 
			Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
			\midrule
			Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
			SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 0.0 & 1.0  \\ 
			Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & 0.0 & 5.0  \\ 
			\midrule 
			Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{114.0} & \textbf{268.0}  \\ 
			Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & 1.65 & 8.58  \\ 
			\bottomrule 
		\end{tabular}

@@

\begin{table}
	\centering
	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleIPC}
	\scalebox{0.7} {
\begin{tabular}{lccccccccccl} 
	\toprule 
	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
	&PO & TO & PO & TO  \\  
	\midrule 
	Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & 0.0 & \textbf{0.72}  \\

	Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & 0.0 & 0.54   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & 0.63   \\ 
	PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.0 & 0.0   \\ 
	Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & 0.0 & \textbf{0.97}  \\ 
	Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.0 & \textbf{1.0}   \\ 
	Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.22 & 0.78   \\ 
	UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & 0.0 & 0.92   \\ 
	Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
	\midrule 
	Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.0 & 0.14   \\ 
	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.0 & 1.0   \\ 
	\midrule 
	IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{1.6} & \textbf{7.9}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}
